Covid-19 A Spatio-Temporal Investigation.

### 2021-01-08 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 O objetivo deste trabalho será portanto traçar um perfil sobre o comportamento espacial da pandemia causada pela Covid-19 ao utilizar de técnicas estatísticas para quantificação da dependência espacial como o cálculo do índice de Moran global e local $\!\!^4$, além de uma estatística de scan para identificação de *clusters* emergentes do número de casos no espaço-tempo, bem como analisar as políticas adotadas por cada país e o comportamento da pandemia ao longo do tempo.

>>>>

 The main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal poisson scan statistic proposed by Kulldorff (place reference here) to identify emerging or "alive" *clusters* in space and time.
